The CrypTool Script: \\ Cryptography, Mathematics and more \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free eLearning program CrypTool\\ (8th edition -- distributed with CrypTool version 1.4.10)} \vspace{60pt}

### 2007-05-22 script/de/script-de.tex
crypto2020 with bibtext added; German Umlaute enabled; some tables narrowed

\documentclass[a4paper,11pt]{article}
% \usepackage[dvips]{graphics}
% \usepackage{graphicx}

@@

% Formatierung der Fu"snoten
\usepackage[flushmargin]{footmisc}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{%\vskip -20 pt 
	{ Das CrypTool-Skript: \\ 
	Kryptographie, Mathematik und mehr} \\
        \vspace{30pt}
        {\large Hintergrundmaterial und Zusatzinformationen\\%*[-8pt]
         zum freien E-Learning-Programm CrypTool\\
         (8. Auflage -- zu Version 1.4.10 Beta 4)}
        \vspace{60pt}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\pagestyle{plain}
\setlength{\fboxrule}{.5mm}
\setlength{\fboxsep}{1.75mm}
\setlength{\footnotesep}{6pt}
\addtolength{\footskip}{8pt}

@@

% Vergleichbar zur Nutzung von Texten aus der Wikipedia (=GNU Free Documentation Licence, GFDL)
\vspace{200pt}
Dies ist ein freies Dokument, d.h. Inhalte des Dokuments k"onnen kopiert und
verbreitet werden, auch zu kommerziellen Zwecken. \\
Im Gegenzug sind Autor, Titel und die CrypTool-Webseite (www.cryptool.de) zu
nennen. Selbstverst"andlich darf aus dem CrypTool-Skript, genau wie aus jedem
anderen Werk auch, zitiert werden. Diese Lizenzbedingungen sind angelehnt an
die GNU-Lizenz f"ur freie Dokumentation.

@@

\input{chapters/introduction.tex}
\input{chapters/cryptomethods.tex}
\input{chapters/paper_and_pencil.tex}
\input{chapters/primes.tex}
\input{chapters/numbertheory.tex}
\input{chapters/moderncryptography.tex}
\input{chapters/digitalsignatures.tex}
\input{chapters/ellipticcurves.tex}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage[latin1]{inputenc} % Umlaute
% \usepackage[dvips]{graphics}
% \usepackage{graphicx}

@@

% Formatierung der Fußnoten
\usepackage[flushmargin]{footmisc}
% Literaturverzeichnis kapitelweise
\usepackage{bibunits}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{%\vskip -20 pt 
	{ Das CrypTool-Skript: \\ 
	Kryptographie, Mathematik und mehr} \\
        \vspace{30pt}
        {\large Hintergrundmaterial und Zusatzinformationen\\%*[-8pt]
         zum freien E-Learning-Programm CrypTool\\
         (8. Auflage -- zu Version 1.4.10)}
        \vspace{60pt}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\pagestyle{plain}
\setlength{\fboxrule}{.5mm}
\setlength{\fboxsep}{1.75mm}
\setlength{\footnotesep}{6pt}
\addtolength{\footskip}{8pt}

@@

% Vergleichbar zur Nutzung von Texten aus der Wikipedia (=GNU Free Documentation Licence, GFDL)
\vspace{200pt}
Dies ist ein freies Dokument, d.h. Inhalte des Dokuments können kopiert und
verbreitet werden, auch zu kommerziellen Zwecken. \\
Im Gegenzug sind Autor, Titel und die CrypTool-Webseite (www.cryptool.de) zu
nennen. Selbstverständlich darf aus dem CrypTool-Skript, genau wie aus jedem
anderen Werk auch, zitiert werden. Diese Lizenzbedingungen sind angelehnt an
die GNU-Lizenz für freie Dokumentation.

@@

\input{chapters/introduction.tex}
\input{chapters/cryptomethods.tex}
\input{chapters/paper_and_pencil.tex}
\input{chapters/primes.tex}
\input{chapters/numbertheory.tex}
\input{chapters/moderncryptography.tex}
\input{chapters/digitalsignatures.tex}
\input{chapters/ellipticcurves.tex}
\bibliographyunit[\section]
\bibliography*{references}
\bibliographystyle*{plain}
\input{chapters/crypto2020.tex}
\bibliographyunit

### 2007-05-22 script/en/chapters/introduction.tex
Script: bugfixes and updates like M44 and Sierpinki
crypto2020 with bibtext added; German Umlaute enabled; some tables narrowed

>>>>

New in May 2007:
- Update for prime records: M44, Sierpinsky, 1039th Mersenne number
- Update for discrete logarithm problem record
- further literature added
- bugfixes reported by readers - thanks.
- new chapter by Prof. Buchmann at al. about current topics in cryptographic
  research and a forecast about the long-term security of cryptographic schemes.

### 2007-05-22 script/en/chapters/numbertheory.tex
crypto2020 with bibtext added; German Umlaute enabled; some tables narrowed

The web pages
\href{http://www.crypto-world.com}{\texttt{http://www.crypto-world.com}}\ 
and
\href{http://www.tutorgig.com/ed/RSA\_number}{\texttt{http://www.tutorgig.com/ed/RSA\_number}}\footnote{%
This site was not quite up-to-date end of May 2005: RSA-200 was missing.}
contain exhaustive overviews about the factoring 
records\index{Factorisation!factoring records} of composed
integers using different methods.

>>>>

An exhaustive overviews about the factoring records\index{Factorisation!factoring records} of 
composed integers using different methods can be found on the following web pages:\\
\href{http://www.crypto-world.com}{\texttt{http://www.crypto-world.com}}\ 
and
\href{http://www.tutorgig.com/ed/RSA\_number}{\texttt{http://www.tutorgig.com/ed/RSA\_number}}\footnote{%
This site was not quite up-to-date end of May 2005: RSA-200 was missing.}
